Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-04-01 W13report.tex
Fixed a (I think) typo in Eqns 2 and 3.  AJC will recheck when he lands.

We model a source--free image (i.e.\ with a background described by a
Gaussian process) using the statistics of Gaussian random fields \citep{Kaiser-PointSources}.  
For an image with Gaussian noise convolved with a
Gaussian PSF with width $\sigma_g$ the density of peaks above a given
detection threshold, $\nu$ is given by 
\begin{equation}
n(>\nu) = \frac{1}{2^{5/2}\pi^{3/2}\sigma_g^{2}} \nu e^{-\nu^2 /2} 
\label{eq-theory}
\end{equation}
 To estimate the number of random
positive detections for a given image we must normalize this density
by the total number of realizations of the PSF within the image, i.e.,
\begin{equation}
N_{total}(>\nu) = n(\nu)*nrow*ncol/PSF_{FWHM}^2
\end{equation}
where nrow and ncol are the number of rows and columns in an images
and $PSF_{FWHM}$ is the FWHM of the PSF.  In difference image analysis, we expect
twice this number, since we are sensitive to both positive and negative--going
fluctuations.

>>>>

We model a source--free image (i.e.\ with a background described by a
Gaussian process) using the statistics of Gaussian random fields \citep{Kaiser-PointSources}.  
For an image with Gaussian noise convolved with a
Gaussian PSF with width $\sigma_g$ the density of peaks above a given
detection threshold, $\nu$ is given by 
\begin{equation}
n(>\nu) = \frac{1}{2^{5/2}\pi^{3/2}\sigma_g^{2}} \nu e^{-\nu^2 /2} 
\label{eq-theory}
\end{equation}
To estimate the number of random
positive detections for a given image we must normalize this density
by the total area of the image, i.e.,
\begin{equation}
N_{total}(>\nu) = n(>\nu) * nrow * ncol 
\end{equation}
where nrow and ncol are the number of rows and columns in an image.  
In difference image analysis, we expect
twice this number, since we are sensitive to both positive and negative--going
fluctuations.
